---
title: "Introduction to GMC"
author: "Xiaoqian Liu, Aaron J. Molstad, and Eric C. Chi"
bibliography: GMC-ref.bib
output:
  html_document: null
  pdf_document: default
  toc: yes
  toc_float:
    collapsed: no
biblio-style: unsrt
vignette: |
  %\VignetteIndexEntry{Introduction to GMC}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---


<style>
img{ background:none; border:none; box-shadow:none; }
</style>

\[
\newcommand{\vbeta}{\boldsymbol{\beta}}
\]

```{r echo=FALSE, cache=FALSE}
set.seed(12345)
knitr::opts_chunk$set(
  cache=TRUE,
  comment = '', 
  fig.width = 5, 
  fig.height = 5,
  fig.align='center'
)
```
## Overview
The `GMC` package implements the group GMC method for grouped variable selection in linear regression proposed  in @Liu-grGMC, which includes GMC for individual variable selection as a special case. The GMC penalization method was originally proposed by @GMC, which is a convex-nonconvex penalization strategy. The main idea of convex-noncovex penalization is to design a nonconvex penalty function while maintaining the convexity of the optimization problem. Motivation of the convex-nonconvex penalization can be found in @GMC and @Liu-grGMC. The group GMC method is a generalization of GMC for grouped variable selection. The `GMC` package implements the group GMC method and provides functions to fit the group GMC model, compute its solution path, and carry out cross-validation. This vignette offers a breif introduction to the basic use of `GMC`.

## Example 

We use a toy simulation example to illustrate how to use the `GMC` package.

```{r}
library(GMC)
set.seed(1234)
n <- 100
p <- 20
# Set the true coefficients
beta <- rep(0, p)
beta[1:8] <- c(1,2,3,4,-1,-2,-3,-4)
# Set the group information: 5 equal length groups
group <- rep(1:5, each=p/5)
# set the group weights
gp <- unique(group)
J <- length(gp)
K <- rep(0,J)
for (j in 1:J) {
  K[j] <- sqrt(length(which(group==gp[j])))
}

# design matrix
X <- matrix(rnorm(n*p), nrow = n)
# response
y <- as.vector(X%*%beta+rnorm(n))
```

To fit a group GMC model, users need to set a value to the convexity-preserving parameter $\alpha$. Typically, we set $\alpha \in (0.5, 1)$. 'GMC' set $\alpha=0.8$ by default. 

```{r}
# fit group GMC at a given lambda value
fit_GMC <- GMC(y=y, X=X, alpha=0.8, group=group, group.multiplier=K, lambdaSeq=0.1, ShowTime=TRUE)
# fit a solution path at a grid of 20 lambda values
path_GMC <- GMC(y=y, X=X, alpha=0.8, group=group, group.multiplier=K, nlambda = 20, ShowTime=TRUE)
```

Note that 'GMC' will automatically compute a $\lambda_{\max}$ which is the samllest $\lambda$ value that produce a zero solution. The generated $\lambda$ sequence from 'GMC' is a decreasing sequence which starts from $\lambda_{\max}$ and ends at $lambda.min*\lambda_{\max}$, where users can specify the ratio 'lambda.min'.

To conduct cross-validation for selecting $\lambda$, users can use the 'cv.GMC' function. 'cv.GMC' provides two rules to select $\lambda$. One is the classical cross-validation, and the other one is the '1se' rule. 

```{r}
# cross-validation
CV_GMC <- cv.GMC(y=y, X=X, alpha=0.8, group=group, group.multiplier=K, nlambda = 20)
# lambda selected by CV
lambda_min <- CV_GMC$lambda_min
# lambda selected by 1se
lambda_1se <- CV_GMC$lambda_1se
```

We compare the solution path of group GMC to those of group Lasso and group MCP (using the 'grpreg' package).

```{r}
path_Lasso <- grpreg(X, y, group, group.multiplier=K, penalty="grLasso")
path_MCP <- grpreg(X, y, group, group.multiplier=K, penalty="grMCP")
# We simply use the unexported function in 'grpreg' to plot the solution paths.
grpreg:::plot.grpreg(path_Lasso)
grpreg:::plot.grpreg(path_MCP)
grpreg:::plot.grpreg(path_GMC)
```

The solution path of group GMC is more flat than the other two, indicating its estimates are less shrunk and it's more robust against the tuning parameter selection. See @Liu-grGMC for more discussion.

## References
